---
title: "Project 2 Draft"
output: html_notebook
---
Is it possible for truffle fermentation systems to mimic the aroma/volatiles of the actual Tuber melanosporum flirting body? 

Given that dimethyl sulfide is one of the most identifying VOCs of Tuber melanosporum, if there is a comparable composition of Dimethyl sulfide in the fermentation broth or mycelia, then the aroma/volatiles should be very similar to that of the actual fruiting body of Tuber melanosporum. 

```{r}
#use function read.csv to read in the csv files and assign them 
broth <- read.csv("broth.csv", row.names = 1)

fruitbody <- read.csv("fruitbody.csv", row.names = 1)

#check the matrixes made in the last lines 
head(broth)
head(fruitbody)

#use function subset to remove extra column from counts dataframe so it matches the 
fruitbody_fixed <- subset(fruitbody, select = -c(MS))

#check new counts dataframe 
head(fruitbody_fixed)

fruitbody_cleaned <- fruitbody_fixed[rowSums(fruitbody_fixed)]

#check counts_cleaned dataframe 
head(fruitbody_cleaned)
```
```

```{r}
#Load in the BiocManager package and the DESeq2 under that to be able to use function DESeqDataSetFromMatrix to turn our matrices into DESeqDataSet object. Install DESeq package. 
library(BiocManager)
BiocManager::install("DESeq2")
library(DESeq2)

#make DESeqDataSet from the matrixes above, using fruitbody_cleaned as the count data and the broth as the column data. 
DESeqDataSet <- DESeqDataSetFromMatrix (countData = fruitbody_cleaned, colData = broth, design = ~condition)

# use DESeq function to analyse the object 
DESeqDataSet <- DESeq(DESeqDataSet)

#print out object to check code
DESeqDataSet

# assign the results of the deseq function to results variable 
results <- results(DESeqDataSet)

#call summary of the results we got from the analysis using function "summary"
summary(results)
```

